---
title: "Problem 6"
author: "Rebeca Lozano"
date: "22/11/2021"
output: pdf_document
---

1. **My simulation on randomly generated data from a normal distribution with n=1000 showed 52/1000 significant p-values. Therefore, it rejected the null hypothesis of normality 5.2% of the time (~5%).**

```{r}
num_rejected <- vector("logical", 1000L)
for (i in 1:1000) {
  x = rnorm(1000)
  test = shapiro.test(x)
  test_results = test$p.value < 0.05
  num_rejected[i] = test_results
}
perc_null_rejected = (length(which(num_rejected=='TRUE'))/1000)*100
```

**2.**

|Distribution|n |1-Bsw|
|-----------:|:-|:---:|
|uniform|10|1-0.925 = 0.075|
|uniform|50|1-0.234 = 0.766|
|uniform|200|1-0 = 1|
|t (dof=3|10|1-0.812 = 0.188|
|t (dof=3)|50|1-0.365 = 0.635|
|t (dof=3)|200|1-0.012 = 0.988|

```{r}
num_rejected_notrejected_1 <- vector("logical", 1000L)
for (i in 1:1000) {
  x_1 = runif(10)
  test_1 = shapiro.test(x_1)
  sw_test_results_1 = test_1$p.value > 0.050
  num_rejected_notrejected_1[i] = sw_test_results_1
}
beta_1 = length(which(num_rejected_notrejected_1=='TRUE'))/1000
power_1 = 1 - (beta_1)

num_rejected_notrejected_2 <- vector("logical", 1000L)
for (i in 1:1000) {
  x_2 = runif(50)
  test_2 = shapiro.test(x_2)
  sw_test_results_2 = test_2$p.value > 0.050
  num_rejected_notrejected_2[i] = sw_test_results_2
}
beta_2 = length(which(num_rejected_notrejected_2=='TRUE'))/1000L
power_2 = 1 - (beta_2)

num_rejected_notrejected_3 <- vector("logical", 1000L)
for (i in 1:1000) {
  x_3 = runif(200)
  test_3 = shapiro.test(x_3)
  sw_test_results_3 = test_3$p.value > 0.050
  num_rejected_notrejected_3[i] = sw_test_results_3
}
beta_3 = length(which(num_rejected_notrejected_3=='TRUE'))/1000
power_3 = 1 - (beta_3)

num_rejected_notrejected_4 <- vector("logical", 1000L)
for (i in 1:1000) {
  x_4 = rt(10,3)
  test_4 = shapiro.test(x_4)
  sw_test_results_4 = test_4$p.value > 0.050
  num_rejected_notrejected_4[i] = sw_test_results_4
}
beta_4 = length(which(num_rejected_notrejected_4=='TRUE'))/1000
power_4 = 1 - (beta_4)

num_rejected_notrejected_5 <- vector("logical", 1000L)
for (i in 1:1000) {
  x_5 = rt(50,3)
  test_5 = shapiro.test(x_5)
  sw_test_results_5 = test_5$p.value > 0.050
  num_rejected_notrejected_5[i] = sw_test_results_5
}
beta_5 = length(which(num_rejected_notrejected_5=='TRUE'))/1000
power_5 = 1 - (beta_5)

num_rejected_notrejected_6 <- vector("logical", 1000L)
for (i in 1:1000) {
  x_6 = rt(200,3)
  test_6 = shapiro.test(x_6)
  sw_test_results_6 = test_6$p.value > 0.050
  num_rejected_notrejected_6[i] = sw_test_results_6
}
beta_6 = length(which(num_rejected_notrejected_6=='TRUE'))/1000
power_6 = 1 - (beta_6)

```


3.

| n1|n2|1-Bks|
|--:|:-|:---:|
|20|20|1-0.96 = 0.04|
|50|50|1-0.926 = 0.074|
|200|200|1 - 0.786 = 0.214|
|500|500|1 - 0.351 = 0.649|

```{r}
library(twosamples)
set.seed(2)
num_rejected_notrejected_7 <- vector("logical", 1000L)
for (i in 1:1000) {
  aa_n1 = runif(20, min = -1.75, max = 1.75)
  aa_n2 = rnorm(20, mean=0, sd=1)
  ks_test_7 = ks.test(aa_n1, aa_n2)
  ks_test_results_7 = ks_test_7$p.value > 0.050
  num_rejected_notrejected_7[i] = ks_test_results_7
}
beta_7 = length(which(num_rejected_notrejected_7=='TRUE'))/1000
power_7 = 1 - (beta_7)
num_rejected_notrejected_8 <- vector("logical", 1000L)
for (i in 1:1000) {
  bb_n1 = runif(50, min = -1.75, max = 1.75)
  bb_n2 = rnorm(50, mean=0, sd=1)
  ks_test_8 = ks.test(bb_n1, bb_n2)
  ks_test_results_8 = ks_test_8$p.value > 0.050
  num_rejected_notrejected_8[i] = ks_test_results_8
}
beta_8 = length(which(num_rejected_notrejected_8=='TRUE'))/1000
power_8 = 1 - (beta_8)
num_rejected_notrejected_9 <- vector("logical", 1000L)
for (i in 1:1000) {
  cc_n1 = runif(200, min = -1.75, max = 1.75)
  cc_n2 = rnorm(200, mean=0, sd=1)
  ks_test_9 = ks.test(cc_n1, cc_n2)
  ks_test_results_9 = ks_test_9$p.value > 0.050
  num_rejected_notrejected_9[i] = ks_test_results_9
}
beta_9 = length(which(num_rejected_notrejected_9=='TRUE'))/1000
power_9 = 1 - (beta_9)
num_rejected_notrejected_10 <- vector("logical", 1000L)
for (i in 1:1000) {
  dd_n1 = runif(500, min = -1.75, max = 1.75)
  dd_n2 = rnorm(500, mean=0, sd=1)
  ks_test_10 = ks.test(dd_n1, dd_n2)
  ks_test_results_10 = ks_test_10$p.value > 0.050
  num_rejected_notrejected_10[i] = ks_test_results_10
}
beta_10 = length(which(num_rejected_notrejected_10=='TRUE'))/1000
power_10 = 1 - (beta_10)
```


4.

| n1|n2|1-Bad|
|--:|:-|:---:|
|20|20|1-0.809 = 0.191|
|50|50|1 - 0.746 = 0.254|
|200|200|1 - 0.315 = 0.685|
|500|500|1 - 0.001 = 0.999|

```{r}
library(twosamples)
num_rejected_notrejected_11 <- vector("logical", 1000L)
for (i in 1:1000) {
  a2_n1 = runif(20, min = -1.75, max = 1.75)
  a2_n2 = rnorm(20, mean=0, sd=1)
  ad_test_11 = as.numeric(ad_test(a2_n1, a2_n2))
  ad_test_results_11 = ad_test_11[2] > 0.050
  num_rejected_notrejected_11[i] = ad_test_results_11
}
beta_11 = length(which(num_rejected_notrejected_11=='TRUE'))/1000
power_11 = 1 - (beta_11)

num_rejected_notrejected_12 <- vector("logical", 1000L)
for (i in 1:1000) {
  b2_n1 = runif(50, min = -1.75, max = 1.75)
  b2_n2 = rnorm(50, mean=0, sd=1)
  ad_test_12 = as.numeric(ad_test(b2_n1, b2_n2))
  ad_test_results_12 = ad_test_12[2] > 0.050
  num_rejected_notrejected_12[i] = ad_test_results_12
}
beta_12 = length(which(num_rejected_notrejected_12=='TRUE'))/1000
power_12 = 1 - (beta_12)

num_rejected_notrejected_13 <- vector("logical", 1000L)
for (i in 1:1000) {
  c2_n1 = runif(200, min = -1.75, max = 1.75)
  c2_n2 = rnorm(200, mean=0, sd=1)
  ad_test_13 = as.numeric(ad_test(c2_n1, c2_n2))
  ad_test_results_13 = ad_test_13[2] > 0.050
  num_rejected_notrejected_13[i] = ad_test_results_13
}
beta_13 = length(which(num_rejected_notrejected_13=='TRUE'))/1000
power_13 = 1 - (beta_13)

num_rejected_notrejected_14 <- vector("logical", 1000L)
for (i in 1:1000) {
  d2_n1 = runif(500, min = -1.75, max = 1.75)
  d2_n2 = rnorm(500, mean=0, sd=1)
  ad_test_14 = as.numeric(ad_test(d2_n1, d2_n2))
  ad_test_results_14 = ad_test_14[2] > 0.050
  num_rejected_notrejected_14[i] = ad_test_results_14
}
beta_14 = length(which(num_rejected_notrejected_14=='TRUE'))/1000
power_14 = 1 - (beta_14)
```

5.
**Based on my results, I would recommend the Anderson-Darling test instead of the KS test because the statistical power of our Anderson-Darling test proved to be greater for all 4 sample sizes, showing it better correctly rejects an incorrect null hypothesis.**

