---
title: "Problem 7"
author: "Rebeca Lozano"
date: "22/11/2021"
output: pdf_document
---

1.
```{r}
stars <- read.csv("stars.csv")
stars$log_luminosity = log(stars$luminosity)
par(mfrow = c(2,2))
plot(stars$distance)
plot(stars$colorindex)
plot(stars$luminosity)
plot(stars$log_luminosity)
par(mfrow = c(1,1))

```


2. 

**a) Distance and luminosity: Spearman correlation coefficient p-value = 0.7612**
  
  **Distance and log_luminosity: Spearman correlation coefficient p-value = 0.7612**
    
**b) Distance and colour index: Spearman correlation coefficient p-value = 0.4728**

**c) Colour index and luminosity: Spearman correlation coefficient p-value = 8.022e-11**
    
  **Colour index and log_luminosity: Spearman correlation coefficient p-value = 8.022e-11**

```{r}

#a
cor.test(stars$distance, stars$luminosity, method='spearman')

cor.test(stars$distance, stars$log_luminosity, method='spearman')

#b
cor.test(stars$distance, stars$colorindex, method='spearman')

#c
cor.test(stars$colorindex, stars$luminosity, method='spearman')

cor.test(stars$colorindex, stars$log_luminosity, method='spearman')

```


3.
```{r}
cols = c('blue','green')
a = as.factor(stars$evoltype)
plot(stars$log_luminosity, stars$colorindex, pch=21, bg = cols[a])

```


4. 

```{r}
stars_wd = stars[stars$evoltype=='WD',]
model_1 = lm(log_luminosity ~ colorindex, data = stars_wd)
summary(model_1)

```

5.
**The colorindex variable is significant, shown by our colourindex p-value of <2e-16. Therefore, it indicates a statistically significant linear relationship.**
```{r}

stars_ms = stars[stars$evoltype=='MS',]
model_2 = lm(log_luminosity ~ colorindex, data = stars_ms)
summary(model_2)

```

6. 
a. $log(luminosity) = 5.1511 - 7.3522(colorindex)$
b. $luminosity = exp(5.1511 - 7.3522(colorindex))$


7.

**a) Our residuals vs. fitted plot shows that we do not have a good residual trend, many of our fitted values deviate from an error of 0. **

**b) Our normal QQ plot shows that our residuals are deviated from normal, as they do not properly follow the line. **

**c) Our red line in our scale-location plot tells us that the average magnitude of the standardized residuals is changing quite plenty as a function of the fitted values, and the spread from the red line tells us that the variability of magnitudes varies strongly as a function of the fitted values.**

**d) Our residuals vs. leverage plot identifies one influential point/outlier (#8) in our model that, if removed, could change the model significantly.**


**No, the assumptions of linear regression are not satisfied under this model.**

```{r}
par(mfrow=c(2,2))
plot(model_2)
par(mfrow=c(1,1))
```

8.
**From our data and model, we gather that SSY = -1786.593, SSM = 750.0742, and SSE = 44.82883.**

```{r}
#a
SSY = sum((stars_ms$log_luminosity - mean(stars_ms$log_luminosity))^2)
SSY
#b
SSM = sum((predict(model_2) - mean(stars_ms$log_luminosity))^2)
SSM
#c
SSE = sum((predict(model_2)-stars_ms$log_luminosity)^2)
SSE
```

9.
**From our data and model, we gather that SSM_3 = 771.5145, and SSE_3 = 23.38856.**
```{r}
model_3 = lm(log_luminosity~colorindex*magnitude, data=stars_ms)
#summary(model_3)

plot(stars_ms$colorindex, stars_ms$log_luminosity)
a <- order(stars_ms$colorindex)
lines(stars_ms$colorindex[a],model_3$fitted[a],col='red',lwd=3)

#par(mfrow = c(2,2))
#plot(model_3)
#par(mfrow = c(1,1))

SSM_3 = sum((predict(model_3)-mean(stars_ms$log_luminosity))^2)
SSM_3
SSE_3 = sum((predict(model_3)-stars_ms$log_luminosity)^2)
SSE_3
```

10.
**From our data and model, we gather that SSM_4 = 767.6827, and SSE_4 = 29.03754.**
```{r}

model_4 = loess(stars_ms$log_luminosity~stars_ms$colorindex,data=stars_ms, span=0.9)
plot(stars_ms$colorindex, stars_ms$log_luminosity)
b <- order(stars_ms$colorindex)
lines(stars_ms$colorindex[b],model_4$fitted[b],col='green',lwd=3)

SSM_4 = sum((predict(model_4) - mean(stars_ms$log_luminosity))^2)
SSM_4

SSE_4 = sum((predict(model_4) - stars_ms$log_luminosity)^2)
SSE_4

```


